ms_figures

### 2023-02-07 ms_figures.Rmd
all figures except for custom artis timeline running

```{r load_data}
# Set directories
datadir <- "outputs"
outdir <- "outputs"
```

@@

```{r fig1, fig.height = 5.75, fig.width = 4.5}
ggarrange(fig1a,
          ggarrange(fig1b,
                    fig1c_out_degree,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("b", "c")),
          ggarrange(fig1d,
                    fig1e,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("d", "e")),
          common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 3, labels = c("a", ""))

@@

```{r fig2, fig.height=5, fig.width=4}
# Overall Figure 2
ggarrange(ggarrange(fig2a, NULL,
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 0.2), labels = c("a", "")), 
          fig2b, labels = c("", "b"),
          ncol = 1, heights = c(1.75, 4))

@@

fig3a <- fig3a_data %>%
  ggplot(aes(x = year, y = supply_per_cap, color = habitat_method)) +
  geom_line() + 
  labs(y = "Per capita supply (kg)", x = "", color = "Source") +
  scale_color_manual(values = habitat_source_colors) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

fig3b <- fig3b_data %>%
  ggplot(aes(x = year, y = supply_per_cap, fill = habitat_method)) +
  geom_area() + 
  labs(y = "Per capita supply (kg)", x = "", fill = "Source") +
  scale_fill_manual(values = habitat_source_colors) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank()) +
  facet_wrap(~region)

@@

```{r fig3}
fig3 <- ggarrange(
  ggarrange(fig3a, fig3b, 
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("a", "b")),
  ggarrange(fig3c, fig3d,
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("c", "d")),
  nrow = 2
)

@@

fig4b <- fig4b_data %>%
  ggplot(aes(x = shannon_supply_domestic, y = shannon_supply_foreign, color = region)) +
    geom_point(alpha = 0.7) +
    geom_abline(slope = 1, intercept = 0) +
  scale_color_manual(values = region_colors) +
  labs(x = "Domestic supply diversity", 
       y = "Foreign supply diversity",
       color = "") +
    theme_minimal()

@@

```{r fig4c}
fig4c_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4c <- fig4c_data %>%
  ggplot(aes(x = imports_live_weight_t/1000000, y = shannon_supply_no_error, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10() +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total imports (million t, live weight)",
       y = "Supply diversity",
       color = "")

@@

```{r fig4, fig.height = 3, fig.width = 3}
fig4 <- ggarrange(fig4a, 
          ggarrange(fig4b,
                    fig4c,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("b", "c")),
          nrow = 2,
          labels = c("a", "", "")
          )

fig4
```

@@

```{r si_top_exporters, fig.height = 4, fig.width = 4}

top_exporters_old <- read.csv(file.path(datadir, "top_exporters_old.csv"))
top_exporters_recent <- read.csv(file.path(datadir, "top_exporters_recent.csv"))

exporters_old_plot <- top_exporters_old %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

exporters_recent_plot <- top_exporters_recent %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

```{r si_top_importers, fig.height = 4, fig.width = 4}

top_importers_old <- read.csv(file.path(datadir, "top_importers_old.csv"))
top_importers_recent <- read.csv(file.path(datadir, "top_importers_recent.csv"))

importers_old_plot <- top_importers_old %>%
  ggplot(aes(x = live_weight_t/1000000, y = importer_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

importers_recent_plot <- top_importers_recent %>%
  ggplot(aes(x = live_weight_t/1000000, y = importer_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

```{r si_regional_changes, fig.height = 4, fig.width = 4}

# Largest regional export changes
top_regional_export_change <- read.csv(file.path(datadir, "top_regional_export_change.csv"))

regional_export_change_plot <- top_regional_export_change %>%
  ggplot(aes(x = change/1000000, y = exporter_region, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=exporter_region, yend=exporter_region)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

# Largest regional import changes
top_regional_import_change <- read.csv(file.path(datadir, "top_regional_import_change.csv"))

regional_import_change_plot <- top_regional_import_change %>%
  ggplot(aes(x = change/1000000, y = importer_region, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=importer_region, yend=importer_region)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

```{r si_export_decreases_increases, fig.height = 4, fig.width = 4}
top_export_increases <- read.csv(file.path(datadir, "top_export_increases.csv"))
top_export_decreases <- read.csv(file.path(datadir, "top_export_decreases.csv"))

exporter_increases_plot <- top_export_increases %>%
  ggplot(aes(x = change/1000000, y = exporter_iso3c, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=exporter_iso3c, yend=exporter_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

exporter_decreases_plot <- top_export_decreases %>%
  ggplot(aes(x = change/1000000, y = exporter_iso3c, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=exporter_iso3c, yend=exporter_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

```{r si_import_decreases_increases, fig.height = 4, fig.width = 4}
top_import_increases <- read.csv(file.path(datadir, "top_import_increases.csv"))
top_import_decreases <- read.csv(file.path(datadir, "top_import_decreases.csv"))

importer_increases_plot <- top_import_increases %>%
  ggplot(aes(x = change/1000000, y = importer_iso3c, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=importer_iso3c, yend=importer_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

importer_decreases_plot <- top_import_decreases %>%
  ggplot(aes(x = change/1000000, y = importer_iso3c, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=importer_iso3c, yend=importer_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

```{r regional_avg_annual_change, fig.height = 4, fig.width = 4}
regional_avg_annual_change <- read.csv(file.path(datadir, "regional_avg_annual_change.csv"))

regional_slopes_ranked <- regional_avg_annual_change %>%
  ggplot(aes(x = slope/1000, y = exporter_importer, color = intraregion)) +
  geom_segment(aes(x=0, xend=slope/1000, y=exporter_importer, yend=exporter_importer, color = intraregion)) +
  geom_point(size=3) +
  scale_y_reordered() +
  scale_color_manual(values = habitat_source_colors[c(1,4)]) +
  labs(y = "", x = "Ave. annual change in export (1000 t live weight)", color = "") +
  theme_minimal() +
  theme(legend.position = "bottom")

>>>>

```{r load_data}
# Set directories
datadir <- "outputs_20230206"
outdir <- "outputs_20230206"
```

@@

```{r fig1, fig.height = 12, fig.width = 7.5}
ggarrange(fig1a,
          ggarrange(fig1b,
                    fig1c_out_degree,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("b", "c")),
          ggarrange(fig1d,
                    fig1e,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("d", "e")),
          common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 3, labels = c("a", ""))

@@

```{r fig2, fig.height=8, fig.width=7}
# Overall Figure 2
ggarrange(ggarrange(fig2a, NULL,
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 0.2), labels = c("a", "")), 
          fig2b, labels = c("", "b"),
          ncol = 1, heights = c(1.75, 4))

@@

fig3a <- fig3a_data %>%
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = supply_per_cap, color = habitat_method)) +
  geom_line() + 
  labs(y = "Per capita supply (kg)", x = "", color = "Source") +
  scale_color_manual(values = habitat_source_colors) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

fig3b <- fig3b_data %>%
   # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = supply_per_cap, fill = habitat_method)) +
  geom_area() + 
  labs(y = "Per capita supply (kg)", x = "", fill = "Source") +
  scale_fill_manual(values = habitat_source_colors) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank()) +
  facet_wrap(~region)

@@

```{r fig3, fig.height = 6, weight = 8}
fig3 <- ggarrange(
  ggarrange(fig3a, fig3b, 
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("a", "b")),
  ggarrange(fig3c, fig3d,
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("c", "d")),
  nrow = 2
)

@@

fig4b <- fig4b_data %>%
  ggplot(aes(x = shannon_domestic, y = shannon_foreign, color = region)) +
    geom_point(alpha = 0.7) +
    geom_abline(slope = 1, intercept = 0) +
  scale_color_manual(values = region_colors) +
  labs(x = "Domestic supply diversity", 
       y = "Foreign supply diversity",
       color = "") +
    theme_minimal()

@@

```{r fig4c_old}
fig4c_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4c <- fig4c_data %>%
  ggplot(aes(x = imports/1000000, y = shannon_supply, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10() +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total imports (million t, live weight)",
       y = "Supply diversity",
       color = "")

@@

```{r fig4, fig.height = 8, fig.width = 12}
fig4 <- ggarrange(fig4a, 
          ggarrange(fig4b,
                    fig4c,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("b", "c")),
          nrow = 2,
          labels = c("a", "", "")
          )

fig4

ggsave(file.path(outdir, "fig4.png"))
```

@@

```{r si_top_exporters, fig.height = 12, fig.width = 5}

top_exporters_old <- read.csv(file.path(datadir, "top_exporters_old.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))
top_exporters_recent <- read.csv(file.path(datadir, "top_exporters_recent.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

exporters_old_plot <- top_exporters_old %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(exporter_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

exporters_recent_plot <- top_exporters_recent %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(exporter_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

```{r si_top_importers, fig.height = 12, fig.width = 5}

top_importers_old <- read.csv(file.path(datadir, "top_importers_old.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))
top_importers_recent <- read.csv(file.path(datadir, "top_importers_recent.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

importers_old_plot <- top_importers_old %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(importer_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

importers_recent_plot <- top_importers_recent %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(importer_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

```{r si_regional_changes, fig.height = 12, fig.width = 5}

# Largest regional export changes
top_regional_export_change <- read.csv(file.path(datadir, "top_regional_export_change.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

regional_export_change_plot <- top_regional_export_change %>%
  ggplot(aes(x = change/1000000, y = reorder(exporter_region, ranking), fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=reorder(exporter_region, ranking), yend=exporter_region)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

# Largest regional import changes
top_regional_import_change <- read.csv(file.path(datadir, "top_regional_import_change.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

regional_import_change_plot <- top_regional_import_change %>%
  ggplot(aes(x = change/1000000, y = reorder(importer_region, change), fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=reorder(importer_region, change), yend=importer_region)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

```{r si_export_decreases_increases, fig.height = 12, fig.width = 5}
top_export_increases <- read.csv(file.path(datadir, "top_export_increases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))
top_export_decreases <- read.csv(file.path(datadir, "top_export_decreases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

exporter_increases_plot <- top_export_increases %>%
  ggplot(aes(x = change/1000000, y = reorder(exporter_iso3c, ranking), fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y= reorder(exporter_iso3c, ranking), yend=exporter_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

exporter_decreases_plot <- top_export_decreases %>%
  ggplot(aes(x = change/1000000, y = reorder(exporter_iso3c, ranking), fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y= reorder(exporter_iso3c, ranking), yend=exporter_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

```{r si_import_decreases_increases, fig.height = 12, fig.width = 5}
top_import_increases <- read.csv(file.path(datadir, "top_import_increases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))
top_import_decreases <- read.csv(file.path(datadir, "top_import_decreases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

importer_increases_plot <- top_import_increases %>%
  ggplot(aes(x = change/1000000, y = reorder(importer_iso3c, ranking), fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y= reorder(importer_iso3c, ranking), yend=importer_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

importer_decreases_plot <- top_import_decreases %>%
  ggplot(aes(x = change/1000000, y = reorder(importer_iso3c, ranking), fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y= reorder(importer_iso3c, ranking), yend=importer_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

```{r regional_avg_annual_change, fig.height = 10, fig.width = 6}
regional_avg_annual_change <- read.csv(file.path(datadir, "regional_avg_annual_change.csv"))

regional_slopes_ranked <- regional_avg_annual_change %>%
  ggplot(aes(x = slope/1000, y = reorder(exporter_importer, slope), color = intraregion)) +
  geom_segment(aes(x=0, xend=slope/1000, y=reorder(exporter_importer, slope), yend=exporter_importer, color = intraregion)) +
  geom_point(size=3) +
  scale_y_reordered() +
  scale_color_manual(values = habitat_source_colors[c(1,4)]) +
  labs(y = "", x = "Ave. annual change in export (1000 t live weight)", color = "") +
  theme_minimal() +
  theme(legend.position = "bottom")
